Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-10-07 manuscript/climate_sensitivity_draft.Rmd
add DOI
#86

### Data and code availability
All data, code, and results are available through the SCBI-ForestGEO organization on GitHub (https://github.com/SCBI-ForestGEO: SCBI-ForestGEO-Data and McGregor_climate-sensitivity-variation repositories), with static versions corresponding to data and analyses presented here archived in Zenodo (DOIs: 10.5281/zenodo.4070038 and *[TBD]*, respectively. Full ForestGEO census data for SCBI are available through the ForestGEO data portal (www.forestgeo.si.edu).

>>>>

### Data and code availability
All data, code, and results are available through the SCBI-ForestGEO organization on GitHub (https://github.com/SCBI-ForestGEO: SCBI-ForestGEO-Data and McGregor_climate-sensitivity-variation repositories), with static versions corresponding to data and analyses presented here archived in Zenodo (DOIs: 10.5281/zenodo.4070038 and 10.5281/zenodo.4070059, respectively. Full ForestGEO census data for SCBI are available through the ForestGEO data portal (www.forestgeo.si.edu).
